%!TEX root = ./M42_Strategy.tex
\chapter{Example Units}
\section{Imperium of Men}
\begin{DndSidebar}{67$^{th}$ Atrian Trenchborn}
\textit{It is said that every third child on the fortress world of Atria is born in a trench to the sound of gunfire and distant artillery.}
\begin{itemize}
	\item \textbf{Type:} Regular Infantry
	\item \textbf{Origin:} Atria System, Atria Sub-Sector
	\item \textbf{Battle Group:} Atria Defense Force 
	\item \textbf{Traits:} Close-Quarter Experts, Siege Experts
\end{itemize}
\end{DndSidebar}

\begin{DndSidebar}{Tigers Argent Tactical Squad}
\textit{The pinnacle of humankind. Post human warriors able to fight in any environment with an unmatched combination of strength, swiftness, precision and shocking brutality.}
\begin{itemize}
	\item \textbf{Type:} Astartes Infantry
	\item \textbf{Origin:} Icefang
	\item \textbf{Battle Group:} 2nd Company under Cpt. Ulfrik 
	\item \textbf{Traits:} Close-Quarter Experts, Know No Fear, Adaptable, Shock Troop Expert, Environmental Sealed
\end{itemize}
\end{DndSidebar}

\begin{DndSidebar}{2$^{nd}$ Maximadin Steel Eaters}
\textit{The Hive forges of this old, gruel and wasted world churn out enclosed armored vehicles and their hardened drivers since even before the days of the Imperium. The 2$^{nd}$ has always been issued with various tank hunting patterns of Leman Russ tanks.}
\begin{itemize}
	\item \textbf{Type:} Armored
	\item \textbf{Origin:} Maximadin System, Sub-Sector SO-400
	\item \textbf{Battle Group:} Imperial Army Task Force under Lord-General Sieng
	\item \textbf{Traits:} Environmental Sealed, Long Range, Anti-Armor, Lengthy Deployment (1)
\end{itemize}
\end{DndSidebar}

\begin{DndSidebar}{Divine Maze}
\textit{This old Mars Alpha pattern cruiser is part of the Sector Battlefleet since four millenia and has a reputation for destroying chaos vessels.}
\begin{itemize}
	\item \textbf{Type:} Navy Cruiser
	\item \textbf{Origin:} Archepex System, Sub-Sector SO-400
	\item \textbf{Battle Group:} Battlefleet Insignitas
	\item \textbf{Traits:} Long Range, Massive Frame, Carrier Craft, Shield Breaker
\end{itemize}
\end{DndSidebar}

\section{Orks}
\begin{DndSidebar}{Ork Boy Mob}
\textit{Numberless greenskin hordes pillage the galaxy in their never ending lust for battle and looting. A large mob of Ork boys is dangerous because of their numbers and brute strength alone.}
\begin{itemize}
	\item \textbf{Type:} Regular Infantry
	\item \textbf{Origin:} Unknown
	\item \textbf{Battle Group:} Waaaagh! Snagrod
	\item \textbf{Traits:} Strength in Numbers, Close Quarter Experts
\end{itemize}
\end{DndSidebar}

\section{Tyranids}
\begin{DndSidebar}{Genestealer Hybrids}
\textit{These vile creatures are from the third generation of the insidious genestealer reproduction cycle and can pass for humans lest for closer inspection. The can use weapons but many still have hidden chitinous armor or a third claw-arm able to rip through steel.}
\begin{itemize}
	\item \textbf{Type:} Regular Infantry
	\item \textbf{Origin:} Cirillo, Cirillo Sub-Sector
	\item \textbf{Battle Group:} Hidden Claw Genestealer Cult
	\item \textbf{Traits:} Close-Quarter Experts, Expandable, Strength in Numbers, Infected
\end{itemize}
\end{DndSidebar}

\section{Chaos}
\begin{DndSidebar}{127${th}$ Panem Rifles}
\textit{Before the opening of the great rift, regiments from the Hive World of Panem were shipped to distant warzones in regular intervals. Recently, the banners of that world have been sighted again but now defiled by the eight-pointed star of chaos. Once proud warriors are now mutated and maddened creatures who threaten to spread their taint to any weak minded souls they encounter.}
\begin{itemize}
	\item \textbf{Type:} Regular Infantry
	\item \textbf{Origin:} Panem, Sub-Sector SO-200
	\item \textbf{Battle Group:} Unknown Chaos Force operating in SO-200
	\item \textbf{Traits:} Anti-Infantry, Expandable, Corrupted
\end{itemize}
\end{DndSidebar}

\begin{DndSidebar}{Plague Bearer Host}
\textit{Bloated inhuman creatures of pestilence bearing wicked crab-claws dripping with diseases and poison surrounded by a nimbus of pest flies.}
\begin{itemize}
	\item \textbf{Type:} Regular Infantry
	\item \textbf{Origin:} Panem, Sub-Sector SO-200
	\item \textbf{Battle Group:} Unknown Chaos Force operating in SO-200
	\item \textbf{Traits:} Shielded (Warp), Shock Troop Expert, Close Combat Experts, Warp Entity, Infected
\end{itemize}
\end{DndSidebar}

\begin{DndSidebar}{Despoiler of Cities}
\textit{This wicked Ravager-class daemon engine is screaming scrap-code alongside volleys of cursed missiles and warp lightning against its enemies. Unstopped it will raze entire cities to the ground and continue its loping walk towards the next until every last trace of civilization is eradicated.}
\begin{itemize}
	\item \textbf{Type:} Battle Titan
	\item \textbf{Origin:} Dread Cloud System, Sub-Sector Fidelis
	\item \textbf{Battle Group:} Despoiler Host (Dark Mechanicus)
	\item \textbf{Traits:} Shielded (Void), Anti-Armor, Shield Breaker, Long Range, Possessed (Undivided), Massive Frame
\end{itemize}
\end{DndSidebar}