

 \section{Commanders \& Heroes}
 Each macro unit has a single commander, responsible for the unit in question. Heroes are highly capable and skilled characters than can be assigned to any unit or even operate alone. Heroes have special actions they can perform depending on their type and provide unique buffs to any unit they are assigned to. \\
 Both, commanders and heroes will accumulate experience as well as traits and advisors depending on their actions, the campaign's they lead or participate in and the due to events.
 
\subsection{Adeptus Astartes}
To be recognized as a commander or hero within the ranks of the superhuman warriors of death, an individual must have breached the pinnacle of his art indeed.\\
\subsubsection{Commanders}
\begin{itemize}
    \item \textbf{Chapter Master:} Powerful, experienced commander with several traits and advisors. Unique within a chapter. Provides a powerful morale boost to all allied units in the same system. May re-roll a fate dice once per year.
    \item \textbf{Captain / Lieutenant:} General space marine commander. Well rounded. Provides morale boost to units under his direct command. Starts with a two random traits.

\end{itemize}
\subsubsection{Heroes}
\begin{itemize}
    \item \textbf{Chaplain:} Extremely capable, fear inducing melee specialist tasked with the mental well-being and loyalty of allies.
    \begin{itemize}
        \item Special Action [Preach]: Greatly improves loyalty and morale of local population or targeted allied unit.
        \item Special Action [Purge]: Reduce CE of an allied unit with the "Corrupted" or "Infected" to remove the effect. CE reduction depends on the severity of the respective effect.
        \item Passive Effect: Morale boost for all allied units on the same battlefield.
        \item Passive Effect: Morale penalty for enemy units subject to fear.
    \end{itemize}
    
    \item \textbf{Librarian:} Powerful psychic combatant, wielding the powers of the warp to destroy the enemy. When activating any of active effect, there is a risk involved of his talents to backfire.
    \begin{itemize}
        \item Special Action [Precognition]: Attempt to divine the strategic moves of the enemy up to a year in advance.
        \item Special Action [Holocaust]: Unleashes a massively powerful psychic firestorm against an enemy unit. Induces direct CE damage to the selected target. Increased damage against units with the [Psyker], [Demonic], [Mutant] or [Tyrannid] trait.
        \item Passive Effect: Detects powerful psychic enemies, performed rituals and large-scale warp movement (e.g. from an approaching fleet) within the sub-sector.
        \item Passive Effect: Shields assigned units from most psychic powers. Reduces the effect of powerful psychic powers on assigned units.
    \end{itemize}

    \item \textbf{Apothecari:} Honor-bound to retrieve the geneseed of fallen brethren as well as to see to the wounded.
    \begin{itemize}
        \item Special Action [Cure]: Attempts to cure one of father Nurgle's many 'gifts' from a target unit or population.
        \item Special Action [Screen]: Increase the chance of the local planet to produce one unit of Neophytes.
        \item Passive Effect: Slightly reduces the CE damage allied units within the same battlefield take from combat.
        \item Passive Effect: Increase the recovery rate of Astartes units in the field by 5\% and aboard the chapter fleet or at a chapter hold by 10 \%.
        \item Passive effect: Increase the chance to recover the geneseed of fallen Astartes (regardless of chapter) on the same battlefield.
    \end{itemize}
    
    \item \textbf{Tech-Marine:} Trained by the Adeptus Mechanicus in the way of the machine god. His task is to oversee the maintenance of the chapters wargear.
    \begin{itemize}
        \item Special Action [Rite of Entombment]: After the death of a Commander, Hero or Veteran-ranked combat squad, the Tech-Marine can perform the rite of entombment, allowing for duty beyond death for his fallen brother. This action triggers a recruitment process with the following specifics: 
        \begin{itemize}
            \item Dreadnought $|$ Assembly $|$ Chapter Hold or Fleet $|$ 1 $|$ Dreadnought Chassis $|$ GG, Rare Minerals $|$ -
        \end{itemize}
        \item Special Action [Artificer Wargear]: Being even less dependant on sleep than his brethren, a Tech-Marine spends any free time on the anvil to produce armour and arms of exceptional quality. In addition to Astartes wargear (see: \ref{recruitment_chart}) a Tech-Marine can also create Terminator armor and dreadnought chassis given enough time and resources. This action triggers one of the following production processes:
        \begin{itemize}
            \item Dreadnought Chassis $|$ Part $|$ Chapter Hold or Fleet $|$ 12 $|$ - $|$ GG, Ore, Rare Minerals $|$ Promethium
            \item Suit of Terminator Armor $|$ Part $|$ Chapter Hold or Fleet $|$ 4 $|$ - $|$ GG, Ore, Rare Minerals $|$ -
        \end{itemize}
        \item Special Action [Fortify]: The Tech-Marine works in concert with chapter Servitors and serfs to create a fortified position on the battlefield (or to reinforce the protection of an existing stronghold). Any such fortified position provides a considerable CE boost to any allied unit defending itself against attacks.
        \item Special Action [Jam]: The Tech-Marine attempts to jam the communication equipment of an enemy macro unit, slightly reducing the CE of all its units for one round. Shock and surprise assaults on a jammed macro unit inflict additional damage.
        \item Passive Effect: Attached Astartes units may recover in the field regardless of their remaining CE, as the Tech-Marine is keeping their equipment in working condition.
        \item Passive effect: Attached Astartes armored units recover 5\% CE in the field, as long as they have more than 50\% CE left.
    \end{itemize}
\end{itemize}

\subsection{Imperial Guard}
\subsubsection{Commanders}
\begin{itemize}
    \item \textbf{Lord General}: Unique commander per sector. Provides a decent morale boost to all allied units within the same system. Starts with two random traits and a random advisor.
    \item \textbf{General}: General macro-unit commander of the imperial guard. Starts with one random trait.
\end{itemize}
\subsubsection{Heroes}
\begin{itemize}
    \item \textbf{Sanctioned Psyker}:
    \item \textbf{Commissar}:
    \item \textbf{Enginseer}:
    \item \textbf{Munitorum Priest}:
\end{itemize}

\subsection{Adeptus Mechanicus}
\subsubsection{Commanders}
\begin{itemize}
    \item \textbf{Magos Militant}:
    \item \textbf{Princeps Maximus}:
\end{itemize}
\subsubsection{Heroes}
\begin{itemize}
    \item \textbf{Magos Biologis}:
    \item \textbf{Magos Ordinatus}:
    \item \textbf{Explorator}:
\end{itemize}

 \subsection{Traits \& Advisors}
 Example Traits:
 \begin{itemize}
     \item \textbf{Defensive Expert:} Increase CE during defensive actions. Gained after several successful defensive battles.
     \item \textbf{Tactical Genius:} May re-roll a fate-dice once per year (must take the second roll). Gained after several decisive victories.
     \item \textbf{Logisticor:} Increase the max supply counter of units under his command by two. Decrease the time required to install a supply depot on a world by one round. Gained after several prolonged wars, where a supply depot had to be installed to keep the units under his command supplied.
 \end{itemize}
 Example Advisors:
 \begin{itemize}
     \item \textbf{Psyker:} May detect rituals, summons, daemons, portals and similar warp-related events early. May occasionally trigger a precognition event.
     \item \textbf{Expert Navigator:} Decreases warp-travel time by one round (min: 1). May detect incoming or outgoing warp travel.
     \item \textbf{Adeptus Titanicus Interfacer:} Specialized Adeptus Mechanicus trained councilor, allowing for better cooperation with Titan elements. Increases CE of units fighting alongside Titans and reduces friendly fire events or its severity.
 \end{itemize}
Some factions have different types of commanders, with varying inherent benefits.